Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-05 GWLDCII.tex
fixed intro and calculation in paper 2

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to \hlfix{space}{I don't know if this was supposed to say ``space'' or ``this space'', and if ``this space'' I don't know which space it's referring to.} \cite{Hodges:2012ym}. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as \hlfix{one expects}{can we call this a conjecture?} the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \hlfix{[ref]}{someone actually proved this, right?}. Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of \hlfix{the space}{help?}; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum. This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto. In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.

@@

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\note{Is the numerator just supposed to be the product of $dc_{pq}$ for each $c_{pq}$ in the matrix? Also I think $c_{46}c_{35} - c_{36}c_{45}$ in the denominator is the wrong way around?}
\end{eg}

>>>>

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as it is conjectured the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \cite{Arkani-Hamed:2013jha}. Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum. This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto. In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.

@@

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}
